Making Sense of Tweets: A framework for individualized student research projects

### 2019-10-09 Rmd/abstract.Rmd
parsed text into one file per section.

To explore social media data science as a pedagogical tool, we developed a teaching and mentoring framework to guide undergraduate researchers through individualized research projects. We demonstrated our approach by guiding two undergraduate researchers while they completed research projects. Our framework involves research question formulation, data acquisition, data analysis and visualization, and presentation of results. Our two student projects, which serve as case studies for our framework, completed all components of the individualized research projects. We found that research skills, self-confidence in research ability, and professional interest in data science increased for both students. Below, we describe our successes, lessons learned, and ideas for others to build similar frameworks for future honors projects.

>>>>

To explore social media data science as a pedagogical tool, we develop
a teaching and mentoring framework to guide undergraduate researchers
through individualized research projects. We demonstrate our approach
by describing our mentoring experience with two undergraduate researchers.
These projects involved Twitter data, Facebook data, topic modeling, and sentiment analysis. Our framework involves research question formulation, data acquisition, data analysis and visualization, and presentation of results. Our two student projects, which serve as case studies for our framework, completed all components of the individualized research projects. We found that research skills, self-confidence in research ability, and professional interest in data science increased for both students. Below, we describe our successes, lessons learned, and ideas for others to build similar frameworks for future honors projects.

### 2019-10-09 Rmd/jse-2019-ms.Rmd
added abstract
fixed title
parsed text into one file per section.

---
title: 'Making Sense of Tweets: Student research projects in data science'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
output: html_document
---

>>>>

---
title: 'Making Sense of Tweets: A framework for individualized student research projects'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
lastmod: "`r lubridate::now()`"
bibliography: jse.bib
output: html_document
---

```{r child = "abstract.Rmd"}
```

```{r child = "introduction.Rmd"}
```

```{r child = "methods.Rmd"}
```

```{r child = "results.Rmd"}
```

```{r child = "discussion.Rmd"}
```

## Discussion

## References
